Temporary Trade Barriers: \\ When Will They End?

### 2018-10-28 outline.tex
add four-stage model (ITC sets AD duties as well as renewal decision) to notes

>>>>

\subsection{Lobbying for the level of $\tau^{AD}$}
This is a four-stage game. The lobby chooses $e^{AD}$ to affect the level of $\tau^{AD}$. Then the ITC chooses $\tau^{AD}$. Then the lobby chooses $e$ to affect the ITC's decision to renew $\tau^{AD}$ or go back to $\tau^a$ and finally the ITC decides whether or not to renew the anti-dumping duties.
\begin{itemize}
	\item ITC's decision to renew the anti-dumping duty or not is a function of lobby's choice of $e \ \left(\frac{\partial r}{\partial e} \neq 0\right)$, it's own $\tau^{ad} \ \left(\frac{\partial r}{\partial \tau^{ad}} \neq 0\right)$, and exogenous $\tau^a, \ga$, and $\pi \ \left(\frac{\partial r}{\partial \tau^a} \neq \frac{\partial r}{\partial \ga} \neq \frac{\partial r}{\partial \pi} \neq  0\right)$:
		\[
		  \frac{\partial r}{\partial e} \frac{\partial e}{\partial \tau^a} + \frac{\partial r}{\partial \tau^a} + \left[ \frac{\partial r}{\partial e} \frac{\partial e}{\partial \tau^{ad}} + \frac{\partial r}{\partial \tau^{ad}}\right] \frac{\partial \tau^{ad}}{\partial \tau^a} + \left[ \frac{\partial r}{\partial e} \frac{\partial e}{\partial \tau^{ad}} + \frac{\partial r}{\partial \tau^{ad}}\right] \frac{\partial \tau^{ad}}{\partial e^{ad}} \frac{\partial e^{ad}}{\partial \tau^a}
		\]
		Where the first three terms are, respectively
			\begin{itemize}
				\item the impact of the lobby's effort decision on the ITC's renew (break) decision
				\item the direct effect of the change in $\tau^a$ on the lobby's effort decision
				\item the direct effect of the change in $\tau^a$ on the ITC's break decision
			\end{itemize}
	\item The lobby makes its decision $e$ as a function of $\tau^{ad} \ \left(\frac{\partial e}{\partial \tau^{ad}} \neq 0\right)$, and exogenous $\tau^a, \ga$, and $\pi \ \left(\frac{\partial e}{\partial \tau^a} \neq \frac{\partial e}{\partial \ga} \neq \frac{\partial e}{\partial \pi} \neq  0\right)$
		\begin{itemize}
			\item The lobby cares that $e$ has an impact on $r$
			\item This is noted by $\frac{\partial r}{\partial e} \neq 0$
		\end{itemize}
	\item If the ITC sets $\tau^{ad}$ in a vacuum, then $\tau^{ad}$ is a function of exogenous $\tau^a, \ga$, and $\pi \ \left(\frac{\partial \tau^{ad}}{\partial \tau^a} \neq \frac{\partial \tau^{ad}}{\partial \ga} \neq \frac{\partial \tau^{ad}}{\partial \pi} \neq  0\right)$
		\begin{itemize}
			\item ITC cares that $\tau^{ad}$ has an impact on $e \ \left( \frac{\partial e}{\partial \tau^{ad}} \neq 0 \right)$
			\item ITC cares that $\tau^{ad}$ has an impact on $r \ \left( \frac{\partial r}{\partial \tau^{ad}} \neq 0, \text{ i.e. } \frac{\partial r}{\partial e}\frac{\partial e}{\partial \tau^{ad}} \neq 0\right)$
		\end{itemize}
	\item Now lobby chooses $e^{ad}$ to influence $\tau^{ad}$. Then $e^{ad}$ is a function of exogenous $\tau^a, \ga$, and $\pi \ \left(\frac{\partial e^{ad}}{\partial \tau^a} \neq \frac{\partial e^{ad}}{\partial \ga} \neq \frac{\partial e^{ad}}{\partial \pi} \neq  0\right)$
		\begin{itemize}
			\item UH OH! I forgot that $e^{ad}$ influences all sorts of things above. Have to fix!
			\item lobby cares that $e^{ad}$ has an impact on $\tau^{ad} \ \left( \frac{\partial \tau^{ad}}{\partial e^{ad}} \neq 0 \right)$
			\item lobby cares that $e^{ad}$ has an impact on $e \ \left( \frac{\partial e}{\partial \tau^{ad}} \frac{\partial \tau^{ad}}{\partial e^{ad}} \neq 0 \right)$
			\item lobby cares that $e^{ad}$ has an impact on $r \ \left( \frac{\partial r}{\partial e^{ad}} \neq 0, \text{ i.e. } \frac{\partial r}{\partial e}\frac{\partial e}{\partial \tau^{ad}} \frac{\partial \tau^{ad}}{\partial e^{ad}} \neq 0\right)$
		\end{itemize}
\end{itemize}
